---
title: "Imposter syndrome"
author: "Henrietta A. Sackey"
format: 
     html:
       toc: true
       toc-depth: 2
       number-sections: true
       number-offset: 3
       toc-location: left
       fontsize: "14"
       include: false
       echo: false
       fig-cap-location: bottom
       tbl-cap-location: top
       author: Henrietta Addai
       self-contained: true

---

```{r}
library(gtsummary)
library(ggpubr)
library(tidyverse)
dset <- read_rds("herty.rds")
```

# Chapter Four - Results

## Demographic characteristics

```{r}
dems <- dset %>% 
  select(age:year) %>% 
  tbl_summary()
```

Most of the respondents were aged between 15 to 20 [`r inline_text(dems, variable = "age", level = "15-20")`] followed by those aged 21-25 [`r inline_text(dems, variable = "age", level = "21-25")`]. Only `r inline_text(dems, variable = "age", level = "15-20")` were 26 or more years old at the time of data collection. The vast majority of the students were single [`r inline_text(dems, variable = "marital", level = "Single")`] with only `r inline_text(dems, variable = "marital", level = "Married")` being married. A lot of the student, `r inline_text(dems, variable = "area", level = "Science")`, identified as pursuing a pure science program (such as chemistry or biology). The remaining student pursued Engineering (`r inline_text(dems, variable = "area", level = "Enginering")`), Mathematics (`r inline_text(dems, variable = "area", level = "Mathematics")`) and Technology (`r inline_text(dems, variable = "area", level = "Technology")`). Of the total respondents, `r inline_text(dems, variable = "year", level = 1)` were in first year, `r inline_text(dems, variable = "year", level = 2)` were in second year, `r inline_text(dems, variable = "year", level = 3)` were in third year, `r inline_text(dems, variable = "year", level = 4)` were in their fourth year and `r inline_text(dems, variable = "year", level = 5)` were in their fifth year or higher.

```{r}
#| label: tbl-dem
#| include: true
#| tbl-cap: Demographic characteristics of respondents 
dems %>% 
  as_gt()
```

## Imposter phenomenon

```{r}
imps <- dset %>% 
  select(eval: study_unable) %>% 
  tbl_summary()
```

Most of the students were indifferent to being evaluated

```{r}
#| include: true
imps
```

